### 2014-06-04 writing/S'14 paper/methods.tex
Adding new Figure 1, updating results on quantifiers.

\begin{figure}[htp]
  \centering
  \includegraphics[scale=0.35]{model.eps}
  \caption{The model structure used to compare \ii{no dog} and \ii{(not all) dog}. 
    The same structure is used for both the RNN and RNTN layer functions.} 
  \label{sample-figure}
\end{figure}

>>>>

\begin{figure}[tp]
  \centering
 % \includegraphics[scale=0.35]{model.eps}

   \scriptsize
\begin{picture}(20,7.5)

  \labeledtreenode[2]{9,7}{$P(\sqsubset) = 0.8$}{softmaxcolor}
  \labeledtreenode[2]{12.5,7}{Softmax classifier}{white}
  \put(10.25,5.98){\vector(0,1){0.88}}

  \labeledtreenode[7]{6.75,5.5}{all reptiles walk \emph{vs.}~some turtles move}{comparisoncolor}
  \labeledtreenode[2]{16,5.5}{Comparison N(T)N layer}{white}

  \put(5.5,4.48){\vector(4,1){3.25}}
  \labeledtreenode{4,4}{all reptiles walk}{compositioncolor}

  \labeledtreenode[2]{9.5,4}{Composition RN(T)N layers}{white}

  \put(3.5,2.98){\vector(2,1){1.7}}
  \labeledtreenode{2,2.5}{all reptiles}{compositioncolor}

  \put(1.5,1.48){\vector(2,1){1.7}}
  \labeledtreenode{0,1}{all}{lexcolor}

  \put(5.5,1.48){\vector(-2,1){1.7}}
  \labeledtreenode{4,1}{reptiles}{lexcolor}

  \put(7.5,2.98){\vector(-2,1){1.7}}
  \labeledtreenode{6,2.5}{walk}{lexcolor}

  \put(15.5,4.48){\vector(-4,1){3.25}}
  \labeledtreenode{14,4}{some turtles move}{compositioncolor}

  \put(13.5,2.98){\vector(2,1){1.7}}
  \labeledtreenode{12,2.5}{some turtles}{compositioncolor}

  \put(11.5,1.48){\vector(2,1){1.7}}
  \labeledtreenode{10,1}{some}{lexcolor}

  \put(15.5,1.48){\vector(-2,1){1.7}}
  \labeledtreenode{14,1}{turtles}{lexcolor}

  \put(17.5,2.98){\vector(-2,1){1.7}}
  \labeledtreenode{16,2.5}{move}{lexcolor}

  \labeledtreenode{5,0.25}{Learned, randomly initialized word vectors}{white}
\end{picture}

  \caption{The model structure used to compare \ii{((all reptiles) walk)} and \ii{((some turtles) move)}. 
    The same structure is used for both the RNN and RNTN layer functions.} 
  \label{sample-figure}
\end{figure}
